### 2013-03-06 doc/final_report/introduction.tex

From the point of view of its users, Partridge was designed to assist
researchers in three principal ways.

\begin{itemize}
\item The system should provide search within specific CoreSC regions of a given
paper. This would allow users to find the most relevant papers to them. For
example a user may search for "mass spectrometer" within the methodology
section of a paper.
\item The system should provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their result, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. 
\item Depending upon the time constraints of the
project, it is hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.

\end{itemize}

>>>>

Partridge is designed to help and facilitate researchers and authors of
scientific papers in the following principal ways:

\begin{itemize}
\item The system should provide search within specific CoreSC regions of a given
paper. This would allow users to find the most relevant papers to them. For
example a user may search for "mass spectrometer" within the methodology
section of a paper.
\item Partridge should allow authors and rightsholders of scientific papers to
upload their papers to the system for inclusion into the search system. This
would give Partridge itself more utility and would make involved authors more
accessible.
\item The system should provide filtering of papers based upon their
specific domain (i.e. is the paper primarily concerned with methodology within
an experiment in chemistry or is it about ethics in psychological studies?) and
their result, whether the paper yielded positive, negative or inconclusive
evidence for a hypothesis. 
\item Depending upon the time constraints of the
project, it was hoped that Partridge will also offer a user 'profiling' system
that provides recommendations for researchers based on their reading history.
This feature should help users find relevant papers more quickly or find
research that they may have otherwise overlooked.a
\end{itemize}

As well as helping users locate files, Partridge will also
